\newcounter{frcount}
\newcommand{\frid}{FR-\ifnum\value{frcount}<10 0\fi\arabic{frcount}}

\newcommand{\fr}[3]{
	\stepcounter{frcount}

	\begin{longtable}{|p{3cm}|p{8cm}|p{3cm}|}
		\hline
		\rowcolor{headergray}
		\textbf{ID} & \textbf{Name} & \textbf{Priority} \\

		\hline
		\frid & {#1} & {#2} \\

		\hline
		\multicolumn{3}{|p{14cm}|}{\textbf{Description:}{#3}} \\
		\hline
	\end{longtable}

	\vspace{1em}
}

\section*{Functional Requirements}

\fr{Login with credentials}{high}
{
The system shall allow users to log in using a username and password or Google account.
}

\fr{Reset password}{High}
{
The system shall allow authenticated users to reset their password via email.
}

\fr{Edit profile}{Medium}
{
The system shall allow authenticated users to edit their profiles, excluding credentials.
}

\fr{Delete profile}{Medium}
{
The system shall allow authenticated users to delete their profiles, should validate exclusion via email.
}

\fr{Add product to cart}{High}
{
The system shall allow authenticated users to add products to their shopping cart.
}

\fr{Remove product from cart}{High}
{
The system shall allow authenticated users to remove products from their shopping cart.
}

\fr{Process Payment}{High}
{
The system shall allow authenticated users to submit payment information to initiate payments through supported payment gateways.
}

\fr{Payment Validation}{High}
{
The system shall validate and confirm payment status before order completion.
}

\fr{Order Tracking}{Medium}
{
The system shall allow authenticated users to view the status and details of their currently active orders.
}

\fr{Orders History}{Low}
{
The system shall allow authenticated users to view their purchase history.
}

\fr{Cancel Order}{Medium}
{
The system shall allow authenticated users to cancel their currently active orders.
}

\fr{Register products}{High}
{
The system shall allow administrators to register products.
}

\fr{Edit products}{High}
{
The system shall allow administrators to edit products.
}

\fr{Delete products}{High}
{
The system shall allow administrators to delete products.
}

\fr{Register stores}{High}
{
The system shall allow administrators to register stores.
}

\fr{Edit stores}{High}
{
The system shall allow administrators to edit stores.
}

\fr{Delete stores}{High}
{
The system shall allow administrators to delete stores.
}

\fr{Register categories}{High}
{
The system shall allow administrators to register categories.
}

\fr{Edit categories}{High}
{
The system shall allow administrators to edit categories.
}

\fr{Delete categories}{High}
{
The system shall allow administrators to delete categories.
}

\fr{Register product sale}{Medium}
{
The system shall allow administrators to register product sales with an optional discount value.
}

\fr{Remove product sale}{Medium}
{
The system shall allow administrators to remove product sales, which will remove all associated links from products, even if the expiration date has not passed.
}

\fr{Link product sales}{Medium}
{
The system will allow administrators to link product sales to products via registration or edit forms, and to add a custom expiration date for each.
}
